\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-04-09 doc/USER_MANUAL/manual_SPECFEM3D.tex
added a note about removing the Unix stack size limit

The SPECFEM3D software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.0.1.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code. To configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran90 compiler and MPI package:

@@

Note that if you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing;
in this case, on some compilers you may need to add \char`\"{}\texttt{-mcmodel=medium}\char`\"{}
to the compiler options otherwise the compiler will display an error message; on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.

>>>>

The SPECFEM3D software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.0.1.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code.\\

We recommend that you add {\texttt{ulimit -S -s unlimited}} to your {\texttt{.bash\_profile}} file and/or {\texttt{limit stacksize unlimited }} to your {\texttt{.cshrc}} file to suppress any potential limit to the size of the Unix stack.\\

Then, to configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran90 compiler and MPI package:

@@

If you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing.
In this case, on some compilers you may need to add \texttt{``-mcmodel=medium}''
to the compiler options otherwise the compiler will display an error
message (for instance \texttt{``relocation truncated to fit: R\_X86\_64\_PC32 against .bss''} or something similar);
on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.
